Music Versus No Music Effectiveness On Cognitive Response Time and Typing Efficiency

### 2024-05-02 Latex Source/paper.tex
start design portion

\subsection[short]{Procedure}
Each participant was instructed to read and then sign the consent form. While the consent form had the basis of what they would be doing, they were given more detail as to the instructions when they were ready to begin.
 %REWRITE THIS HERE
%First they would take the short typing test three times to account for the three levels of music. 
%They would then do a QBTest three times again for the music. 
%The eye tracker is mounted around a laptop stand and the laptop is placed in between the stand so that the screen is behind the eyetracker.
The two computers were set up side by side so that it would be easy for the participant to switch between the typing test and QBTest.
This setup also made it simple for the music component as the participants did each level together (e.g. the no music level was typing test 
then the QBTest) before moving on to the next level.

>>>>

\subsection[short]{Procedure}
Each participant was instructed to read and then sign the consent form. While the consent form had the basis of what they would be doing, they were given more detail as to the instructions when they were ready to begin.
 %REWRITE THIS HERE
%First they would take the short typing test three times to account for the three levels of music. 
%They would then do a QBTest three times again for the music. 
%The eye tracker is mounted around a laptop stand and the laptop is placed in between the stand so that the screen is behind the eyetracker.
The two computers were set up side by side so that it would be easy for the participant to switch between the typing test and QBTest.
This setup also made it simple for the music component as the participants did each level together 
(e.g. typing test then QBTest without having to change the music or swapping to no music)
before moving on to the next level. 
Because of the way that the heatmap was coded, we had to make sure that each level was done in the same order for all the participants.
We made sure to always do instrumental music, lyrical music, then no music.
